Trajectories

### 2022-08-22 docs/index.Rmd
Add index.Rmd
Clean manuscript folder

```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# set params
tar_load_globals()
tar_load_all()
theme_set(theme_custom())

@@

by_class <- items %>% 
  drop_na(frequency, class) %>% 
  ggplot(aes(frequency, lv, fill = class, colour = class)) +
  facet_wrap(vars(class), ncol = 2) +
  geom_point(alpha = 0.25, shape = 1, stroke = 1, show.legend = FALSE) +
  labs(y = "Levenshtein similarity", x = "Lexical frequency", colour = "cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = percent)

>>>>

```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# set params
tar_load_all()
theme_set(theme_custom())
```

@@

by_class <- items %>% 
    drop_na(frequency, class) %>% 
    ggplot(aes(frequency, lv, fill = class, colour = class)) +
    facet_wrap(vars(class), ncol = 2) +
    geom_point(alpha = 0.25, shape = 1, stroke = 1, show.legend = FALSE) +
    labs(
        y = "Levenshtein similarity",
        x = "Lexical frequency", 
        colour = "cognateness", 
        fill = "Cognateness"
    ) +
    scale_y_continuous(labels = percent)
